\section{List Structure}
\subsection{List structures}
\paragraph{Three enviroment:}
\begin{itemize}
	\item[-] itemize.
	\item[-] enumerate.
	\item[-] description.
\end{itemize}
\paragraph{Lists format:}
All lists follow the basic format:
\begin{verbatim}
	\begin{list_type}
	\item	The first item.
	\item	The second item.
	\item	The third.
	\item	etc \ldots
	\end{list_type}
\end{verbatim}

\subsubsection{Itemize}
\paragraph{}
This enviroment is for your standard bulleted list of items.
The results is looks like this:
\begin{itemize}
	\item 1st item.
	\item 2nd item.
	\item 3rd item.
\end{itemize}
Or you can modify a bit, as below:
\begin{verbatim}
\begin{itemize}
	\item[+] 1st item.
	\item[+] 2nd item.
	\item[+] 3rd item.
\end{itemize}
\end{verbatim}
And the result would looks like this:
\begin{itemize}
	\item[+] 1st item.
	\item[+] 2nd item.
	\item[+] 3rd item.
\end{itemize}
or:
\begin{itemize}
	\item[$\rightarrow$] 1st item.
	\item[$\rightarrow$] 2nd item.
	\item[$\rightarrow$] 3rd item.
\end{itemize}
Can you guess how to make a result as right above?

\subsubsection{Enumerate}
\paragraph{}
The enumerate enviroment is for ordered lists, where by defult,
each item is numbered sequentially.\\
The result:
\begin{enumerate}
	\item 1st item.
	\item 2nd item.
	\item 3rd item.
\end{enumerate}

\subsubsection{Description}
\paragraph{}
The description enviroment is slightly different.
You can specify the item label by passing it as optional argument
(although optional, it would look odd if you didn't include it!). Ideal for
a series of definitions, such as a glossary.
\paragraph{}
Example:
\begin{verbatim}
\begin{description}
	\item[First:] 1st item.
	\item[Second:] 2nd item.
	\item[Third:] 3rd item.
\end{description}
\end{verbatim}
and the result:
\begin{description}
	\item[First:] 1st item.
	\item[Second:] 2nd item.
	\item[Third:] 3rd item.
\end{description}

\paragraph{}
Sometimes you want a description where the text begins on a new line.
This cannot easily be done with \verb|\\|. The trick is to use
\verb|\hfill|.
\begin{verbatim}
\begin{description}
	\item[First:] \hfill \\ 1st item.
	\item[Second:] \hfill \\ 2nd item.
	\item[Third:] \hfill \\ 3rd item.
\end{description}
\end{verbatim}
and the result:
\begin{description}
	\item[First:] \hfill \\ 1st item.
	\item[Second:] \hfill \\ 2nd item.
	\item[Third:] \hfill \\ 3rd item.
\end{description}

\subsection{Compacted lists}
\paragraph{}
In standard \LaTeX{} document classes, the vertical spacing between items,
and above and below the list as a whole, is more than between paragraphs:
it may look odd if the descriptions are too short. If you want tightly-packed
lists, use the \verb|mdwlist| (\verb|mdwtools| bundle), which provides
compact, ``starred'' versions of ther previous enviroments, i.e.
\verb|itemize*|, \verb|enumerate*|, \verb|description*|. They work exactly
in the same way, but the output is more compact.\\
Other packages: \verb|paralist|, \verb|enumitem|.

\subsection{Nested lists}
\paragraph{}
\LaTeX{} will happily allow you to insert a list enviroment in to an existing
one (up to a depth of 4 -- if you need more than four, use the
\verb|easylist| package).
\paragraph{}
Simply begin the appropriate enviroment at the desired point within the
current list. \LaTeX{} will sort out the layout and any numbering for you.
\begin{verbatim}
\begin{enumerate}
	\item 1st item.
		\begin{enumerate}
			\item 1st nested item.
			\item 2nd nested item.
			\item 3rd nested item.
		\end{enumerate}
	\item 2nd item.
	\item 3rd item.
\end{enumerate}
\end{verbatim}
%----
\begin{enumerate}
	\item 1st item.
\begin{enumerate}
	\item 1st nested item.
	\item 2nd nested item.
	\item 3rd nested item.
\end{enumerate}
	\item 2nd item.
	\item 3rd item.
\end{enumerate}

\subsection{Customizing lists}
\paragraph{}
Customizing \LaTeX ~is outside the beginners' domain. While not necessarily
difficult in itseld, because beginners are already overwhelmed with the array
of commands and enviroments, moving on to more advanced topics runs the risk
of confusion.
\paragraph{}
However, since the tutorial is on formatting, I shall still include a brief
guide on customizing lists. Feel free to skip!

\subsubsection[Line spaces]{Customizing line spacing in lists}
\paragraph{}
Inside lists you can redefine some leghth/dimension varibles of \LaTeX~, for
example using:
\begin{verbatim}
\begin{itemize}
	\itemsep1pt \parskip0pt \parsep0pt
	\item The first item.
	\item The second item.
\end{itemize}
\end{verbatim}
the result: more nicely!
\begin{itemize}
	\itemsep1pt \parskip0pt \parsep0pt
	\item The first item.
	\item The second item.
\end{itemize}
\paragraph{}
Alternatively, to create a unified look in your document you can define your
own enumerate enviroment:
\begin{verbatim}
	\newenvironment{my_enumerate}
		{\begin{enumerate}
			\setlength{\itemsep}{1pt}
			\setlength{\parskip}{0pt}
			\setlength{\parsep}{0pt}}
		{\end{enumerate}}
\end{verbatim}
And let try it: more nicely too!
\newenvironment{my_enumerate}
	{\begin{enumerate}
		\setlength{\itemsep}{1pt}
		\setlength{\parskip}{0pt}
		\setlength{\parsep}{0pt}
	\end{enumerate
}
\begin{my_enumerate}
	\item First item.
	\item Second item.
\end{my_enumerate}

\subsubsection[Enumerated lists]{Customizing enumerated lists}
\paragraph{}
The thing people want to change most often with Enumerated lists are the
counters. A quick solution to this problem is provided by the \verb|enumerate|
package of David Carlisle, or the more sophisticated package \verb|enumitem|
by Javier Bezos.
\paragraph{}
To go any further and do it yourseld instead, a brief instroduction to \LaTeX{} \emph{couters} is required. For anything that \LaTeX ~automatically numbers,
such as section headers, figures, and itemized lists, there is a counter
associated with it that controls the numbering.
\paragraph{}
There a four individual counters that are associated with itemized lists,
each one represents the four possible levels of nesting, which are called:
\begin{my_enumerate}
	\item \verb|enumi|.
	\item \verb|enumii|.
	\item \verb|enumiii|.
	\item \verb|enumiv|.
\end{my_enumerate}
In order to reset any of these counters in the middle of an enumeration
simply use \verb|\setcounter|. The counter is incremented by \verb|\item|
before it is printed.
\subparagraph{}
For example to reset \verb|enumi| use:
\begin{verbatim}
\begin{enumerate}
	\setcounter{enumi}{4}
	\item Fifth element.
\end{enumerate}
\end{verbatim}
and will get the result:
\begin{enumerate}
	\setcounter{enumi}{4}
	\item Fifth element.
\end{enumerate}

\paragraph{}
Each counter also has a default format that dictates how it is displayed
whenever \LaTeX{} needs to print it. Such formats are specified using internal
\LaTeX{} commands:
\begin{itemize}
	\itemsep1pt \parskip0pt \parsep0pt
	\item \verb|\arabic| $\rightarrow$ 1, 2, 3 \ldots
	\item \verb|\alph| $\rightarrow$ a, b, c \ldots
	\item \verb|\Alph| $\rightarrow$ A, B, C \ldots
	\item \verb|\roman| $\rightarrow$ i, ii, iii, ldots
	\item \verb|\Roman| $\rightarrow$ I, II, III, ldots
	\item \verb|\fsymbol| $\rightarrow$ Aimed at footnotes (see blow), but
		prints a sequence of symbols.
\end{itemize}

\paragraph{}
Each counter entity holds various bits of information about itself. To get
to the numbered element, simply use \verb|the| flollowed immediately
(i.e., no space) by the name of the counter, e.g., \verb|\theenumi|.
This often referred to as the \emph{representation} of a counter.
\paragraph{}
Now, that's most of the techicalities out of the way. To make changes to
the formatting of a given level:\newline
\verb|\renewcommand{\representation}{\format_command{counter}}|\newline
Examples:
\begin{verbatim}
%Redefine the first level:
\renewcommand{\theenumi}{\Roman{enumi}}
\renewcommand{\labelenumi}{\theenumi}

%Redefine the second level:
\renewcommand{\theenumii}{\Alpha{enumii}}
\renewcommand{\labelenumii}{\theenumii}
\end{verbatim}

%Redefine the first level:
\renewcommand{\theenumi}{\roman{enumi}}
\renewcommand{\labelenumi}{\theenumi}

%Redefine the second level:
\renewcommand{\theenumii}{\alph{enumii}}
\renewcommand{\labelenumii}{\theenumii}
the result:
\begin{enumerate}
	\item Level 1: 1st item.
\begin{enumerate}
	\item Level 2: 1st nested item.
	\item Level 2: 2nd nested item.
	\item Level 2: 3rd nested item.
\end{enumerate}
	\item Level 1: 2nd item.
	\item Level 1: 3rd item.
\end{enumerate}

\paragraph{}
The method used above first explicitly changes the format used by counter.
However, ther element that controls the label needs to be updated to reflect
the change, which is what the second line does. Another way to achieve this
result is this:
\begin{verbatim}
\renewcommand{\labelenumi}{\roman{enumi}}
\end{verbatim}
This simply redefine the appearance of the label, which is fine, providing
that you do not intend to cross-reference to a specific item within the list,
in which case the reference will be printed in the previous format. This
issue does not arise in the first example.
Example:
\begin{verbatim}
\renewcommand{\labelenumi}{\roman{enumi}}
\renewcommand{\labelenumii}{\alph{enumii}}
\begin{enumerate}
	\item Level 1: 1st item.
\begin{enumerate}
	\item Level 2: 1st nested item.
	\item Level 2: 2nd nested item.
	\item Level 2: 3rd nested item.
\end{enumerate}
	\item Level 1: 2nd item.
	\item Level 1: 3rd item.
\end{enumerate}
\end{verbatim}
the result:
\renewcommand{\labelenumi}{\roman{enumi}}
\renewcommand{\labelenumii}{\alph{enumii}}
\begin{enumerate}
	\item Level 1: 1st item.
\begin{enumerate}
	\item Level 2: 1st nested item.
	\item Level 2: 2nd nested item.
	\item Level 2: 3rd nested item.
\end{enumerate}
	\item Level 1: 2nd item.
	\item Level 1: 3rd item.
\end{enumerate}

\paragraph{}
Note that you can also ad other symbols, such as parentheses and periods,
before and affter the counter. For instance, to create a list indexed by
a lower case letters with parentheses before and after the letter, you
might enter the following:
\begin{verbatim}
\renewcommand{\labelenumi}{\roman{enumi}.}
\renewcommand{\labelenumii}{-\alph{enumii}-}
\end{verbatim}
the result:
\renewcommand{\labelenumi}{\roman{enumi}.}
\renewcommand{\labelenumii}{-\alph{enumii}-}
\begin{enumerate}
	\item Level 1: 1st item.
\begin{enumerate}
	\item Level 2: 1st nested item.
	\item Level 2: 2nd nested item.
	\item Level 2: 3rd nested item.
\end{enumerate}
	\item Level 1: 2nd item.
	\item Level 1: 3rd item.
\end{enumerate}

\subsubsection[Itemised lists]{Customizing itemised list}
\paragraph{}
Itemised lists are not as complex as they do not need to count. Therefore,
to customize, you simply change the labels. It can be done manully for each
entry with \verb|\item[new symbol]|, eg \verb|\item[$star$]|.
\paragraph{}
The itemize labels are accessed via:
\begin{itemize}
	\itemsep1pt \parskip0pt \parsep0pt
	\item[---] \verb|\labelitemi|
	\item[---] \verb|\labelitemii|
	\item[---] \verb|\labelitemiii|
	\item[---] \verb|\labelitemiv|
\end{itemize}
for the four respective levels.
\begin{verbatim}
\renewcommand{\labelitemi}{$\star$}
\end{verbatim}
the result:
\renewcommand{\labelitemi}{$\star$}
\begin{itemize}
	\itemsep1pt \parskip0pt \parsep0pt
	\item \verb|\labelitemi|
	\item \verb|\labelitemii|
	\item \verb|\labelitemiii|
	\item \verb|\labelitemiv|
\end{itemize}

\paragraph{}
Itemised list with tightly set items, that is no vertial space between two
consecutive items, can be created as follows:
\begin{verbatim}
\begin{itemize}
	\setlength{\itemsep}{0cm}%
	\setlength{\parskip}{0cm}%
	\item[-] \labelitemi
	\item[-] \labelitemii
	\item[-] \labelitemiii
	\item[-] \labelitemiv
\end{itemize}
\end{verbatim}
the result:
\begin{itemize}
	\setlength{\itemsep}{0cm}%
	\setlength{\parskip}{0cm}%
	\item[-] \verb|\labelitemi|
	\item[-] \verb|\labelitemii|
	\item[-] \verb|\labelitemiii|
	\item[-] \verb|\labelitemiv|
\end{itemize}
\subsubsection[Details of customizing]{Details of customizing lists}
\paragraph{}
Note that is is necessary that the \verb|\renewcommand| appears after the\\
\verb|\begin{document}| instruction so the changes made are taken into
account. This is needed for both enumerate and itemized lists.

\subsection{Inline lists}
\paragraph{}
Inline lists are a special case as they require the use of the
\verb|paralist| package which provides the \verb|inparaenum| enviroment
(with an optional formatting specification in square brackets, i.e: 
\verb|\begin{inparaenum}[(\alph)]|):
\subparagraph{Example:}
\begin{verbatim}
\textbf{\itshape Inline lists},
which are sequential in nature, just like
enumerated lists, but are
\begin{inparaenum}[\itshape \alph\upshape)]
\item formatted within their paragraph;
\item usually labelled with letters; and
\item usually have the final item prefixed with `and' or `or',
\end{inparaenum}
like this example\ldots
\end{verbatim}

\textbf{\itshape Inline lists}, which are sequential in nature, just like
enumerated lists, but are
\begin{inparaenum}[\itshape a\upshape)]
\item formatted within their paragraph;
\item usually labelled with letters; and
\item usually have the final item prefixed with `and' or `or',
\end{inparaenum}
like this example\ldots
\paragraph{}
Other packages providing inline lists are \verb|shortlst| and \verb|enumitem|.
